Massively Parallel Learning for Penalized Logistic Regression Model

### 2013-06-02 draft.tex
add graphs

\section{Experiments} \label{sec:experiment}
In this section, we conduct an empirical analysis of our algorithms.
Particularly, we illustrate test errors in terms of accuracy and convergence in terms of MAP, both with respect to running time.

We choose five open datasets to run all four test programs:	
The	Simulated \textbf{2d} dataset has 2 features and 200 instances.
The	\textbf{20NewsGroup} dataset has 16428 features and 1988 instances. We split it into a training set of 1800 instances and a test set of 188 instances.	
The	third test dataset is the \textbf{Gisette}~\cite{guyon2004result} dataset, which has 5000 features and 7000 instances. We split it into a training set of 6000 instances and a test set of 1000 instances.
The	fourth test dataset is the \textbf{ECUESpam}~\cite{DelanyKBS05} dataset, which has 100249 features and 10678 instances (after proper preprocessing). We split it into a training set of 9000 instances and a test set of 1687 instances.
Finally, we have the \textbf{URL-Reputation}~\cite{ma2009identifying} dataset, which has 3231961 features and 2376130 instances. We split it into a training set of 2356130 instances and a test set of 20000 instances.
We randomly repeat such split 20 times and our analysis is based on the average performance of 20 repetitions.

\begin{table}[h]
\centering
\caption{Datasets}\label{tab:table1}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
    Name           & \# of Feat. & \# of Inst. & Sparsity & \# of Nonzeros & \# of +1 Inst. / \# of -1 Inst.\\
\hline
    2d             & 2             & 200            & ...      & ...                 & 1.000 \\
\hline
    20NewsGroup    & 16428         & 1988           & ...      & ...                 & 1.006 \\
\hline
    Gisette        & 5000          & 7000           & ...      & ...                 & 1.000 \\
\hline
    ECUESpam       & 100249        & 10678          & ...      & ...                 & 5.882 \\
\hline
    URL-Reputation & 3231961       & 2376130        & ...      & ...                 & ... \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Cluster Information}\label{tab:table2}
\begin{tabular}{|c|c|}
\hline
    CPU Model & ... \\
\hline
    Number of node & 6 \\
\hline
    Number of CPU per node & 8\\
\hline
    Memory per node & 12G \\
\hline
    Disk per node & 2T \\
\hline
    Cache Size per node & ... \\
\hline
\end{tabular}
\end{table}

\comment{Will add more on experimental results later in next version of draft}

@@

\comment{3: add 5 line graphs;one dataset each;x:iteration number;y:MAP;6 lines}

@@

\comment{further parallelization in PSUBPLR-MR, Primal Map is the bottleneck}
\comment{parameter passing issues in PSUBPLR-MR, the effect in small dataset}
\comment{MR job start time}
Analysis points:

@@

\begin{table}[h]
\centering
\caption{Accuracy Result}\label{tab:table3}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
\hline
Mahout     & 93.5\% & 71.3\% & 91.5\% & 85.2\% & 91.5\% \\
\hline
Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & 96.2\% \\
\hline
Sublinear  & 93.5\% & 91.5\% & 94.8\% & 92.3\% & 94.2\% \\
\hline
PSublinear & 93.5\% & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
\hline
Spark      & 93.5\% & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
\hline
subSpark   & 93.5\% & 90.5\% & 95.8\% & 91.7\% & 94.0\% \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Running Time Result}\label{tab:table4}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
\hline
Mahout     & 0.595s & 9.827s & 131.807s & 96.611s & 10100.209s \\
\hline
Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & 519.115s \\
\hline
Sublinear  & 1.761s & 20.046s & 130.451s & 1028.185s & 3248.473s \\
\hline
PSublinear & 120.186s & 1360.854s & 3687.941s & 11478.706s & 16098.260s \\
\hline
Spark      & 0.681s & 10.517s & 99.156s & 924.020s & 3615.780s \\
\hline
subSpark   & 1.325s & 8.571s & 89.094s & 796.802s & 2918.470s \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Fault Tolerance}\label{tab:table5}
\begin{tabular}{|c|c|c|}
\hline
           & System Level & Algorithm Level \\
\hline
Mahout     & \Checkmark & \XSolid  \\
\hline
Liblinear  & \XSolid & \XSolid \\
\hline
Sublinear  & \XSolid & \Checkmark \\
\hline
PSublinear & \Checkmark & \Checkmark \\
\hline
Spark      & \Checkmark & \XSolid \\
\hline
subSpark   & \Checkmark &  \Checkmark \\
\hline
\end{tabular}
\end{table}

@@

2d-dataset (separation graph)
\begin{figure}[tb] \label{fig:02}
\center \includegraphics[height=5cm,width=7cm]{show-2d.png}
\caption{2d Dataset, Visual Result}
\end{figure}

>>>>

\section{Experiments} \label{sec:experiment}
In this section, we conduct an empirical analysis of our algorithms.

We choose five open datasets to run all six test programs:	
The	Simulated \textbf{2d} dataset has 2 features and 200 instances.
The	\textbf{20NewsGroup} dataset has 16428 features and 1988 instances. We split it into a training set of 1800 instances and a test set of 188 instances.	
The	third test dataset is the \textbf{Gisette}~\cite{guyon2004result} dataset, which has 5000 features and 7000 instances. We split it into a training set of 6000 instances and a test set of 1000 instances.
The	fourth test dataset is the \textbf{ECUESpam}~\cite{DelanyKBS05} dataset, which has 100249 features and 10678 instances (after proper preprocessing). We split it into a training set of 9000 instances and a test set of 1687 instances.
Finally, we have the \textbf{URL-Reputation}~\cite{ma2009identifying} dataset, which has 3231961 features and 2376130 instances.
We split it into a training set of 2356130 instances and a test set of 20000 instances.
Apart from the Simulated \textbf{2d} dataset, other four datasets are all sparse. Details are shown in Table~\ref{tab:table1}.
We randomly repeat such split 20 times and our analysis is based on the average performance of 20 repetitions.

%Particularly, we illustrate test errors in terms of accuracy and convergence in terms of MAP, both with respect to running time.

\begin{table}[h]
\centering
\caption{Datasets}\label{tab:table1}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
    Name           & \# of Feat. & \# of Inst. & Sparsity & \# of Nonzeros & \# of +1 Inst. / \# of -1 Inst.\\
\hline
    2d             & 2             & 200            & 1.0                  & 400                 & 1.000 \\
\hline
    20NewsGroup    & 16428         & 1988           & $7.384\times10^{-3}$ & 238511              & 1.006 \\
\hline
    Gisette        & 5000          & 7000           & 0.12998              & 4549319             & 1.000 \\
\hline
    ECUESpam       & 100249        & 10687          & $2.563\times10^{-3}$ & 2746159             & 5.882 \\
\hline
    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-35}$ & 277058644           & 0.500 \\
\hline
\end{tabular}
\end{table}

The cluster that we implement on has the following configurations shown in Table~\ref{tab:table2}.
\begin{table}[h]
\centering
\caption{Cluster Information}\label{tab:table2}
\begin{tabular}{|c|c|}
\hline
    CPU Model & Intel Xeon E5-1410: 2.80GHz \\
\hline
    Number of node & 6 \\
\hline
    Number of CPU per node & 4 Cores, 8 Threads \\
\hline
    RAM per node & 16G \\
\hline
    Disk per node & 4T HDD\\
\hline
    Interconnection Method & Gigabyte Ethernet  \\
\hline
\end{tabular}
\end{table}

2d-dataset (separation graph)
\begin{figure}[tb] \label{fig:02}
\center \includegraphics[height=5cm,width=7cm]{img/show-2d.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:03}
\center \includegraphics[height=4.5cm,width=6cm]{img/2d_accuracy_iteration.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:04}
\center \includegraphics[height=4.5cm,width=6cm]{img/20NewsGroup_accuracy_iteration.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:05}
\center \includegraphics[height=4.5cm,width=6cm]{img/Gisette_accuracy_iteration.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:6}
\center \includegraphics[height=4.5cm,width=6cm]{img/ECUESpam_accuracy_iteration.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:07}
\center \includegraphics[height=4.5cm,width=6cm]{img/URL-Reputation_accuracy_iteration.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:08}
\center \includegraphics[height=5cm,width=10cm]{img/all_time.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:09}
\center \includegraphics[height=5cm,width=10cm]{img/2d_time.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:10}
\center \includegraphics[height=5cm,width=10cm]{img/20NewsGroup_time.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:11}
\center \includegraphics[height=5cm,width=10cm]{img/Gisette_time.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:12}
\center \includegraphics[height=5cm,width=10cm]{img/ECUESpam_time.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:13}
\center \includegraphics[height=5cm,width=10cm]{img/URL-Reputation_time.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\begin{figure}[tb] \label{fig:14}
\center \includegraphics[height=5cm,width=10cm]{img/fault_tolerance.png}
\caption{2d Dataset, Visual Result}
\end{figure}

@@

%\comment{3: add 5 line graphs;one dataset each;x:iteration number;y:MAP;6 lines}

@@

\comment{further parallelization in PSUBPLR-MR, Primal Map is the bottleneck}
\comment{parameter passing issues in PSUBPLR-MR, the effect in small dataset}
\comment{MR job start time}
\comment{baseline liblinear}
\comment{2d test method}
\comment{not all converge at the iteration shown}
\comment{symbol review}
\comment{single reducer of spark}
\comment{Iteration Number for SLLR explain}
\comment{Liblinear Url result}
\comment{fault tolerance: on url dataset,6 nodes}
Analysis points:

@@

\begin{table}[h]
\centering
\caption{Accuracy Result}\label{tab:table3}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
\hline
Mahout     & 93.5\% & 71.3\% & 91.5\% & 85.2\% & 91.5\% \\
\hline
Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & $96.2\%^*$ \\
\hline
SLLR       & 93.5\% & 91.5\% & 94.8\% & 92.3\% & 94.2\% \\
\hline
PSUBPLR-MR & 93.5\% & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
\hline
PGDPLR-SPARK & 93.5\% & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
\hline
PSUBPLR-SPARK & 93.5\% & 90.5\% & 95.8\% & 91.7\% & 94.0\% \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Running Time Result}\label{tab:table4}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
\hline
Mahout     & 0.595s & 9.827s & 131.807s & 96.611s & 10100.209s \\
\hline
Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & $519.115s^*$ \\
\hline
SLLR       & 1.761s & 20.046s & 130.451s & 1028.185s & 3248.473s \\
\hline
PSUBPLR-MR & 120.186s & 1360.854s & 3687.941s & 11478.706s & 16098.260s \\
\hline
PGDPLR-SPARK & 0.681s & 10.517s & 99.156s & 924.020s & 3615.780s \\
\hline
PSUBPLR-SPARK & 1.325s & 8.571s & 89.094s & 796.802s & 2918.470s \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Fault Tolerance}\label{tab:table5}
\begin{tabular}{|c|c|c|}
\hline
           & System Level & Algorithm Level \\
\hline
Mahout     & \Checkmark & \XSolid  \\
\hline
Liblinear  & \XSolid & \XSolid \\
\hline
SLLR  & \XSolid & \Checkmark \\
\hline
PSUBPLR-MR & \Checkmark & \Checkmark \\
\hline
PGDPLR-SPARK & \Checkmark & \XSolid \\
\hline
PSUBPLR-SPARK & \Checkmark &  \Checkmark \\
\hline
\end{tabular}
\end{table}

@@
